\documentclass[10pt]{article}

\usepackage[brazilian, english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=2cm]{geometry}

\begin{document}

\title{Resume}

\author{Thiago Messias Simões de Freitas Bonfim}

\date{\today}

% ==================================================

\begin{center}

\section*{Thiago Messias Simões de Freitas Bonfim}

\subsection*{Resume}

\noindent\\
Brazilian, 30 years old.\\

Budapest, Hungary\\

+36 70 242 9210\\~\\
\emph{bonfimtm@gmail.com}\\
\emph{bonfimtm.com}\\
\emph{linkedin.com/in/bonfimtm}\\
\emph{github.com/bonfimtm}\\

\end{center}

% ==================================================

\section*{Education}

Bachelor in Computer Engineering at Vale do São Francisco Federal University (UNIVASF) in Juazeiro, Brazil. Science Without Borders Exchange Program at Óbuda University, Kandó Kálmán Faculty of Electrical Engineering, in Budapest, Hungary.

% ==================================================

\section*{Profile}

\begin{itemize}
	\item Main experience in Web Development and Embedded Systems Test Automation;
    \item C, C++, Java, Python, JavaScript, TypeScript, PHP, Swift, HTML, CSS, SQL;
    \item Embedded Systems: CAN, FlexRay, XCP, AUTOSAR;
    \item Front End: Bootstrap, AngularJS, Angular, Vue, Ionic, jQuery, JSP, JSF, Facelets and PrimeFaces;
    \item Back End: Java EE, JPA, Hibernate, Spring, Firebase, PostgreSQL, MySQL, Oracle Database and DB2;
    \item ISTQB Foundation Level Certified Tester;
    \item Fluent English and native Portuguese.
\end{itemize}

% ==================================================

\section*{Professional Experience}

\begin{enumerate}

	\item \textbf{Software Test Engineer - thyssenkrupp Components Technology Hungary Kft.}
	\begin{itemize}
		\item March 2017 - Currently -- Budapest, Hungary;
		\item Automated Integration Testing of Embedded Systems Software for Electric Power Assisted Steering (EPAS) systems;
		\item Python, C, CAN, FlexRay, XCP, AUTOSAR.
	\end{itemize}

	\item \textbf{Full Stack Web Developer - MV Informática Nordeste Ltda.}
	\begin{itemize}
		\item October 2016 - December 2017 (3 months) -- Recife, Brazil;
		\item Health management systems developer;
	    \item Spring Framework, Hibernate, AngularJS and Oracle Database.
	\end{itemize}

	\item \textbf{Systems Analyst / Developer - Linx S.A.}
	\begin{itemize}
		\item April 2016 - September 2016 (6 months) -- Recife, Brazil;
		\item Commercial Automation Systems projects web and desktop developer;
		\item Java EE, Hibernate, AngularJS and DB2.
	\end{itemize}

	\item \textbf{Full Stack Web Developer - Secretaria da Fazenda do Estado de Pernambuco / Third Party}
	\begin{itemize}
		\item May 2015 -- March 2016 (11 months) -- Recife, Brazil;
		\item Software developer on corporate systems for Secretaria da Fazenda do Estado de Pernambuco - Sefaz/PE;
		\item Java EE, AngularJS and Oracle Database.
	\end{itemize}

	\item \textbf{Full Stack Web Developer -- Department of Distance Education of Vale do São Francisco Federal University / Third Party}
	\begin{itemize}
		\item January 2013 - June 2013 (6 months) -- Petrolina, Brazil;
		\item Web application development to manage teachers' and coordinators' reports of distance education courses of Vale do São Francisco Federal University (UNIVASF);
		\item Java Web, JSF, Primefaces, MySQL.
	\end{itemize}

	\item \textbf{Computer Technician -- Infoloja}
	\begin{itemize}
		\item February 2007 - June 2007 (5 months) -- Senhor do Bonfim, Brazil;
		\item Responsible for assembly, maintenance, and installation of desktop computers.
	\end{itemize}

\end{enumerate}

% ==================================================

\section*{Scientific Experience}

\begin{itemize}\item \textbf{Scientific Initiation Scholarship -- PIBIC/Univasf}
	\begin{itemize}
		\item August 2011 - July 2012 (1 year) -- Juazeiro, Brazil;
		\item Application of a parallel programming model with multi-cores of a massively parallel model using Graphics Processing Units (GPUs) in an Two Variables Polynomial Regression Algorithm which implements a terrain shape modeling of the region of São Francisco Valley.
	\end{itemize}

	\item \textbf{Scientific Initiation Scholarship -- PIBIC/CNPq}
	\begin{itemize}
		\item August 2010 - July 2011 (1 year) -- Juazeiro, Brazil;
		\item Development of a tool to evaluate the quality of requirement documents.
	\end{itemize}

	\item \textbf{Scientific Initiation Scholarship -- PIBIC/FAPESB}
	\begin{itemize}
		\item August 2009 - July 2010 (1 year) -- Juazeiro, Brazil;
		\item Extension of the management software of health entities CIDHA e VIPEPI in Juazeiro -- BA, Brazil.
	\end{itemize}

	\item \textbf{Scientific Initiation Scholarship -- PIBIC/CNPq}
	\begin{itemize}
		\item August 2008 - July 2009 (1 year) -- Juazeiro, Brazil;
		\item Development of management software for health entities CIDHA and VIPEPI in Juazeiro, Brazil.
	\end{itemize}

	\item \textbf{Main Papers and Book Chapters}:

	\begin{enumerate}
		
		\item BONFIM, T. M. S. F. ; RAMOS R. A. ; LEAL, B. G. . DEVELOPMENT OF A MUSICAL CHORDS RECOGNIZER SYSTEM. Cluj-Napoca, Romania. XIX FIATAL M\H{U}SZAKIAK TUDOMÁNYOS \"{U}LÉSSZAKA, v. 19, p. 97-100, 2014. \textbf{ISSN 2067 - 6 808}.

		\item BONFIM, T., NERY FILHO, J., RAMOS R. and BORATTO, M., The barracuda design pattern (in Portuguese). In: Proceedings of the 9th Latin-American Conference on Pattern Languages of Programming. New York, NY, USA: ACM, 2012. (SugarLoafPLoP '12), p. 7:1--7:13. DOI 10.1145/2591028.2600816. \textbf{ISBN 978-1-4503-2787-9}. Disponível em:\\ http://doi.acm.org/10.1145/2591028.2600816.
		
		\item BORATTO, M. C. ; LEAL, B. ; BARRETO, M. ; COELHO, L. ; BONFIM, T. M. S. F. . Modelagem Computacional da Espacialização do Relevo na Região Agrícola do Vale do Rio São Francisco. In: Paulo Sausen; Airam Sausen. (Org.). Pesquisas Aplicadas em Modelagem Matemática. 1ed.Ijuí: Unijuí, 2012, v. 1, p. 81-101. \textbf{ISBN: 9788541900379}.

	\end{enumerate}

\end{itemize}

% ==================================================

\begin{flushright}
\textbf{
	\\~\\
	\noindent
	Thiago Messias Simões de Freitas Bonfim\\
	Budapest, \today
}
\end{flushright}

\end{document}
